% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org

% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca

% (c) 2008 Nathaniel Johnston <nathaniel@nathanieljohnston.com> http://www.nathanieljohnston.com

% (c) 2011 Scott Clark <sc932@cornell.edu> http://cam.cornell.edu/~sc932
% (c) 2012 Phillip Baker <pbaker@retrodict.com> https://phillbaker.com

%This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 2.5 License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter to Creative Commons, 543 Howard Street, 5th Floor, San Francisco, California, 94105, USA.

%TODO I'd like something to do prioritized scaling of font size, margins, line heights, spacing between letters, etc. to automagically fit stuff into 1 page - like every resume should be (if you're not succinct, appear to be); doesn't look like that's easy (adjustbox didn't do it):
% http://tex.stackexchange.com/questions/13107/adding-a-cost-of-extra-pages-forcing-a-page-limit
% http://tex.stackexchange.com/questions/19347/is-there-any-package-to-automatically-select-font-size-and-margins-to-optimize
%TODO Styling: http://loftresumes.com/, http://dominicp.com/dp/wp-content/uploads/2011/01/Dominic_Prestifilippo_Resume.pdf, http://www.nicolascoia.com/wp-content/uploads/2011/08/NicolasCoia_Resume_2011.pdf


\documentclass[letterpaper,1opt]{article}
\newlength{\outerbordwidth}
\pagestyle{empty}
\raggedbottom
\raggedright
\usepackage[svgnames]{xcolor}
\usepackage{framed}
\usepackage{tocloft}
\usepackage{fullpage}
%\usepackage{amsmath}
%\usepackage{amsfonts}
%\usepackage{mathtools}
%\usepackage{graphicx}
\usepackage{url}
\usepackage{soul}
%TODO force 1 page, scale the fonts sizes/margins
%\usepackage[totalheight=11in]{geometry}
%\usepackage{helvet}

%-----------------------------------------------------------
% Headings setup
\setlength{\outerbordwidth}{3pt}  % Width of border outside of title bars
\definecolor{shadecolor}{gray}{0.75}  % Outer background color of title bars (0 = black, 1 = white)
\definecolor{shadecolorB}{gray}{0.93}  % Inner background color of title bars

%-----------------------------------------------------------
% Margin setup
\setlength{\evensidemargin}{-0.25in}
\setlength{\headheight}{-0.25in}
\setlength{\headsep}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\tabcolsep}{0in}
\setlength{\textheight}{9.75in}
\setlength{\textwidth}{7in}
\setlength{\topmargin}{-0.3in}
\setlength{\topskip}{0in}
\setlength{\voffset}{0.1in}

%-----------------------------------------------------------
% Custom commands

\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}

\newcommand{\resheading}[1]{\vspace{8pt}
  \parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}
    \begin{shaded}
\setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.762in][l]{\large #1} \vphantom{p\^{E}}}}}}
    \end{shaded}
  }\vspace{-5pt}
}

\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}

\newcommand{\jobheading}[4]{
\begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}

%-----------------------------------------------------------

\begin{document}

		\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
			\textbf{\Large Phillip Baker} 								& \textbf{\today} 			\\
			Graduate Student, University of Pennsylvania 	& pbaker@retrodict.com 	\\
			Philadelphia, PA 															& (408) 904-9404 				\\
		\end{tabular*}

		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

		\resheading{Education}

		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		
		%I'm a little funky: straight through, 5 years undergrad/grad, all from the same university, same grad date, so lump it together...
		\ressubheading{University of Pennsylvania}{Philadelphia, Pennsylvania}{}{}

		\begin{itemize}

		\item
			\begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep} \extracolsep{\fill}}r}
					\textbf{The Jerome Fisher Program in Management and Technology} & Graduating May 2012 \\
					\textit{Electrical Engineering, Bachelor of Science in Engineering} & \\
					\textit{Management \& Finance, Wharton School, Bachelor of Science in Economics} & \\
			\end{tabular*}\vspace{-6pt}

			\begin{itemize}
				\resitem{Semester Abroad, Hong Kong University of Science and Technology 				2009}
				\resitem{Teaching Assistant, Management of Technology Wharton School 		 2010 - 2012}
				\resitem{GPA 3.45/4.0, Dean's List 2010-11}
			\end{itemize}

		\item
			\ressubheading{ Masters of Science in Engineering, Integrated Product Design}{Graduating May 2012}{}{}

			\begin{itemize}
				\resitem{GPA 3.66/4.0}
			\end{itemize}

		\end{itemize}
					   
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

		\resheading{Employment}

		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

		\begin{itemize}
		%summer after senior year
		%Finance Rotation Program
		\item \jobheading{Intern}{Microsoft}{Redmond, Washington}{Summer 2011}
			Conducted a strategy review of business model innovation for the Startup Business Group by analyzing companies and synthesizing patterns across the diverse industries and firm sizes. Created learning materials and presented findings to the group.

		%summer after junior year
		\item \jobheading{Technology Summer Analyst}{Goldman Sachs}{New York, New York}{Summer 2010}
			Re-engineered the Technology division’s business-process surrounding 5000 desk and office seats with the Chief of Staff team. Created a monthly report to show quantitative usage of office-space inventory reducing uncertainty about the division’s 2nd largest expense and aiding office-space planning.

		%summer after sophomore year
		\item \jobheading{Business Intelligence Intern}{Federal Home Loan Bank of New York}{New York, New York}{Summer 2009}
			As a member of the Business Intelligence data-warehouse team, implemented 3 iterations of a data quality analysis tool in Groovy using Agile with Scrum development practices. Identified integration errors in the \$27 billion/year collateral system and contributed to issue resolution. 

		%summer after freshman year
		\item \jobheading{Summer Intern}{QED Benchmark Capital Management}{San Francisco, California}{Summer 2008}
			Developed a web-based Ruby-on-Rails application to back-test users’ investment strategies over a 24 million row data-warehouse of more than 250 financial metrics. Designed hardware, system infrastructure, and database administration. Interviewed applicants in the hiring process in order to continue the product. 

		%gap year
		\item \jobheading{Associate Engineer}{Product Systems Inc.}{Campbell, California}{Fall, 2006 - Spring, 2007}
			Designed, developed and tested 12,000 lines of Java code in a quality assurance and research and development scanning system. Validated products’ specifications and mapped products’ energy output in 3D. 

		\end{itemize}
		
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

		\resheading{Leadership \& Achievements}

		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

		\begin{itemize}
			\item \jobheading{Co-founder of Verday}{}{}{Fall 2010 – Spring 2011}
				This web-based venture created financial and social incentives to reduce personal energy usage, winning over \$13,000 in prize money from business plan competitions, including 1st undergrad team in the Wharton Business Plan Competition, 2nd place in PennVention and 1 of 10 slots in the Venture Initiation Program incubator. 
			
			\item \jobheading{Philadelphia Marathon}{}{}{Fall 2010}
				Trained for and completed my first marathon in 2 hours, 49 minutes to place in the top 1\% of race finishers.
			
			\item \jobheading{Eagle Scout Troop 566}{}{Saratoga, California}{2006}
		\end{itemize}

		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

		\resheading{Technical Experience}

		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

		\begin{itemize}
			\item \jobheading{Wikipedia Spam Detection}{}{}{2010-2011}
				A multi-threaded, real-time data-collection system storing metadata and HTML source of external links added to the English-language Wikipedia. Responsible for threading and queuing in 3 person team. Ruby, MySQL.
				Published in: WikiSym '11: Proceedings of the Seventh International Symposium on Wikis and Open Collaboration. October 2011. 
			
			\item \jobheading{JetDesk Mobile App}{}{}{Spring 2012}
				Created wireframes and developed a HTML5 and JQuery Mobile app for employee collaboration, hot-desk reservation and furniture maintenance as part of a thesis project on designing smart office furniture. PhoneGap, Android, iOS.
			
			\item \jobheading{Lumin Biosensors}{}{}{Winter 2010}
				Built service infrastructure in a 3-person team building interactive data visualizations of 12,000 reports to evaluate the government water quality reporting system of the West Bengal (India). Python, Ruby, SQLite.
		
			\begin{itemize}
				\resitem{Languages: Ruby, Java, PHP, C, others}
				\resitem{Databases: MySQL, SQLite, Oracle}
				\resitem{{\mdseries(github.com/phillbaker)}}
			\end{itemize}

		\end{itemize}
		
\end{document}
